\vspace{-0.8in}Brief Announcement: A Family of Leaderless Generalized-Consensus Algorithms

### 2016-02-13 podc16/paper2.tex
minor fix

We show that the core idea underlying EPaxos can be captured in a generic leaderless generalized consensus algorithm that uses two new abstractions: a \textit{dependency-set algorithm}, which suggests dependencies for commands, and a \textit{map-agreement algorithm}, which ensures that, for each submitted command, processes agree on a dependency set. Both abstractions lend themselves well to implementations that avoid the use of a unique leader process.
Our generic algorithm gives rise to a family of algorithms whose members are obtained by using a concrete map-agreement algorithm and a concrete dependency-set algorithm. 
%Note that any generalized consensus algorithm can be used to implement (2), but only a weaker problem than generalized consensus needs to be solved because no ordering among proposal is required.

>>>>

We show that the core idea underlying EPaxos can be captured in a \emph{generic leaderless generalized consensus algorithm} that uses two new abstractions: a \textit{dependency-set algorithm}, which suggests dependencies for commands, and a \textit{map-agreement algorithm}, which ensures that, for each submitted command, processes agree on a dependency set. Both abstractions lend themselves well to implementations that avoid the use of a unique leader process.
Our generic algorithm gives rise to a family of algorithms whose members are obtained by using a concrete map-agreement algorithm and a concrete dependency-set algorithm. 
%Note that any generalized consensus algorithm can be used to implement (2), but only a weaker problem than generalized consensus needs to be solved because no ordering among proposal is required.
